---
title: "Nous Data Analytics: Student-Teacher Ratios"
format: revealjs
---
```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
data <- read_csv("nous.csv")
colnames(data)[2] <- "State"
colnames(data)[5] <- "ST_Ratio"
```

## Research Question

How has the student-teacher ratio in Queensland's government-run high schools compared over time with:

- Other school affiliations within Queensland
- Schools in NSW and Victoria

## Part 1 — Queensland School Affiliations
```{r QLD-data}
QLD_all <- data %>%
  filter(State == "QLD")
```

The mean student-teacher ratio in Queensland is **`r round(mean(QLD_all$ST_Ratio), 1)`** — meaning for every teacher, there are ~14 students.

## QLD Ratios by Affiliation (Bar)
```{r QLD-bar}
ggplot(QLD_all, aes(x = factor(Year), y = ST_Ratio, fill = Affiliation)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "Year", y = "Student-Teacher Ratio",
       title = "Student-Teacher Ratios by Affiliation in QLD") +
  theme_minimal()
```

## QLD Ratios by Affiliation (Trend)
```{r QLD-line}
ggplot(QLD_all, aes(x = Year, y = ST_Ratio, color = Affiliation, group = Affiliation)) +
  geom_point(size = 3) +
  geom_line(size = 1) +
  labs(x = "Year", y = "Student-Teacher Ratio",
       title = "Student-Teacher Ratios by Affiliation in Queensland") +
  theme_minimal()
```